\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{nohyperref}
\usepackage{float}
\newcommand{\BibTeX}{\textrm{B \kern -.05em \textsc{i \kern -.025em b} \kern -.08em
T \kern -.1667em \lower .7ex \hbox{E} \kern -.125emX}}
\begin{document}

    \title{Mining Massive Data Sets Endterm Report}

    \author{
        \IEEEauthorblockN{1\textsuperscript{st} Luong Canh Phong}
        \IEEEauthorblockA{
            \textit{Faculty of Information Technology} \\
            \textit{Ton Duc Thang University}\\
            Ho Chi Minh City, Vietnam \\
            522H0036@student.tdtu.edu.com
        }
        \and
        \IEEEauthorblockN{2\textsuperscript{nd} Cao Nguyen Thai Thuan}
        \IEEEauthorblockA{
            \textit{Faculty of Information Technology} \\
            \textit{Ton Duc Thang University}\\ \
            Ho Chi Minh City, Vietnam \\
            522H0092@student.tdtu.edu.com
        }
        \and
        \IEEEauthorblockN{3\textsuperscript{rd} Tang Minh Thien An}
        \IEEEauthorblockA{
            \textit{Faculty of Information Technology} \\
            \textit{Ton Duc Thang University}\\
            Ho Chi Minh City, Vietnam \\
            522H0075@student.tdtu.edu.com
        }
        \and
        \IEEEauthorblockN{4\textsuperscript{th} Truong Tri Phong}
        \IEEEauthorblockA{
            \textit{Faculty of Information Technology} \\
            \textit{Ton Duc Thang University}\\
            Ho Chi Minh City, Vietnam \\
            522H0167@student.tdtu.edu.com
        }
        \and
        \IEEEauthorblockN{5\textsuperscript{th} Instructor: Nguyen Thanh An}
        \IEEEauthorblockA{
            \textit{Faculty of Information Technology} \\
            \textit{Ton Duc Thang University}\\
            Ho Chi Minh City, Vietnam \\
            nguyenthanhan@tdtu.edu.com
        }
    }

    \maketitle

    \begin{abstract}
        This project implements and evaluates key techniques in mining massive datasets.
        It covers hierarchical agglomerative clustering of string shingles using Jaccard distance; PySpark-based linear regression for gold price prediction;
        CUR decomposition for feature dimensionality reduction on gold price data; and PageRank analysis of the \texttt{it.tdtu.edu.vn} web graph using PySpark.
        The work demonstrates practical applications and provides insights into processing large-scale data.
    \end{abstract}


    \section{Introduction}
    \label{sec:introduction}
    The increasing volume of data requires efficient mining techniques.
    This project implements and analyzes four core algorithms: (1) hierarchical agglomerative clustering for non-Euclidean text data, using 4-shingles and Jaccard distance on alphabetical strings; (2) PySpark-based linear regression to predict Vietnamese gold prices from historical data; (3) CUR decomposition to reduce the dimensionality of gold price features (from 10 to 5) and assess its impact on regression; and (4) PageRank, implemented in PySpark, to identify influential pages within the \texttt{it.tdtu.edu.vn} web graph.
    Python and PySpark are utilized throughout.
    This report details the methodologies, implementations, and experimental results for each task.


    \section{First Task: Hierarchical clustering in non-Euclidean spaces}
    \label{sec:first-task}
    \input{sections/first-task}


    \section{Second Task: Linear Regression – Gold price prediction}
    \label{sec:second-task}
    \input{sections/second-task}


    \section{Third Task: CUR – Dimensionality Reduction}
    \label{sec:third-task}
    \input{sections/third-task}


    \section{Fourth Task: PageRanking – the Google algorithm}
    \label{sec:fourth-task}
    \input{sections/fourth-task}


    \section{Contribution}
    \label{sec:contribution}

    The following table represents the contribution of each member, note that whichever member handles whichever task will also write the report for that task.

    \begin{table}[h]
        \centering
        \caption{Member Contributions}
        \setlength{\tabcolsep}{2pt} % Reduce column spacing
        \renewcommand{\arraystretch}{1} % Adjust row spacing
        \resizebox{\linewidth}{!}{ % Fit within column width
            \begin{tabular}{|l|c|c|c|}
                \hline
                \textbf{ID} & \textbf{Member}       & \textbf{Contribution}      & \textbf{Progress} \\
                \hline
                522H0036    & Luong Canh Phong      & Task 2 and Handling Report & 100\%             \\
                522H0092    & Cao Nguyen Thai Thuan & Task 4 and Report Support  & 100\%             \\
                522H0075    & Tang Minh Thien An    & Task 3                     & 100\%             \\
                522H0167    & Truong Tri Phong      & Task 1                     & 100\%             \\
                \hline
            \end{tabular}
        }
        \label{tab:contributions}
    \end{table}


    \section{Self-evaluation}
    \label{sec:self-evaluation}

    The following table is our self-evaluation on our tasks:

    \begin{table}[h]
        \centering
        \caption{Self-evaluation}
        \setlength{\tabcolsep}{2pt} % Reduce column spacing
        \renewcommand{\arraystretch}{1} % Adjust row spacing
        \resizebox{\linewidth}{!}{ % Fit within column width
            \begin{tabular}{|l|c|c|c|}
                \hline
                \textbf{Task} & \textbf{Task Requirements}                      & \textbf{Completion Ratio} \\
                \hline
                Task 1        & Hierarchical clustering in non-Euclidean spaces & 90\%                      \\
                Task 2        & Linear Regression – Gold price prediction       & 100\%                     \\
                Task 3        & CUR – Dimensionality Reduction                  & 90\%                      \\
                Task 4        & PageRanking – the Google algorithm              & 100\%                     \\
                Task 5        & Report                                          & 100\%                     \\
                \hline
            \end{tabular}
        }
        \label{tab:self-evaluation}
    \end{table}


    \section{Conclusion}
    \label{sec:conclusion}
    This project successfully fulfilled the end-term requirements for Mining Massive Data Sets.
    Key tasks, all leveraging PySpark, included implementing hierarchical clustering with Jaccard distance for textual data, developing a linear regression model for gold price prediction, exploring CUR dimensionality reduction, and applying the PageRank algorithm to a crawled web graph.
    Analysis of experimental results from each module offered practical insights into algorithm efficacy.
    Overall, this project provided significant hands-on experience, reinforcing theoretical concepts and demonstrating our group's ability to apply these complex data mining techniques to diverse problems.

    \begin{thebibliography}{00}
        \bibitem{b1}
        \textit{PySpark Overview — PySpark 3.5.5 documentation}.
        (n.d.). https://spark.apache.org/docs/latest/api/python/index.html

        \bibitem{b2}
        GeeksforGeeks.
        (2025, February 4). \textit{Hierarchical clustering in machine learning}.
        GeeksforGeeks.
        https://www.geeksforgeeks.org/hierarchical-clustering/

        \bibitem{b3}
        Wikipedia contributors.
        (2025, April 11). \textit{Jaccard index}.
        Wikipedia.
        https://en.wikipedia.org/wiki/Jaccard\_index

        \bibitem{b4}
        \textit{API Reference — PySpark 3.5.5 documentation}.
        (n.d.). https://spark.apache.org/docs/latest/api/python/reference/index.html

        \bibitem{b5}
        Mahoney, M. W., \& Drineas, P. (2009).
        CUR matrix decompositions for improved data analysis. \textit{Proceedings of the National Academy of Sciences}, \textit{106}(3), 697–702.
        https://doi.org/10.1073/pnas.0803205106

        \bibitem{b6}
        GeeksforGeeks.
        (2025b, April 15). \textit{Page rank Algorithm and Implementation}.
        GeeksforGeeks.
        https://www.geeksforgeeks.org/page-rank-algorithm-implementation/
    \end{thebibliography}
\end{document}